
#Libraries
```{r}
#start-->20:47
library(ggplot2)
library(data.table)
library(magrittr)
# Needed for %>% operator
library(tidyr)
library(ggbeeswarm)
```

#Q1
1. shows distribution and quantiles, especially useful when comparing distributions. --> box plot
2. highlights individual values, supports comparison and can show rankings or deviations categories and totals --> bar chart
3. shows overall changes and patterns, usually over intervals of time--> line chart
4. shows relationship between two continues variables.--> scatter plot

#Q2
```{r}
iris_dt<-as.data.table( iris)

dim(iris_dt)
head(iris_dt)

```

#Q3
```{r}
iris_melt <- melt(iris_dt, id.vars = "Species")
iris_melt
ggplot(iris_melt, aes(x=value) ) + geom_histogram()+ facet_wrap(~variable) + theme_bw()
```

#Q4
```{r}
ggplot(iris_melt, aes(x=value) ) + geom_histogram(bins = 20)+ facet_wrap(~variable) + theme_bw()
```

#Q5
```{r}
box_visual<-ggplot(iris_melt, aes(x=variable,y=value )) + theme_bw()
box_visual + geom_boxplot()
box_visual + geom_boxplot() +geom_jitter(alpha=0.3)
box_visual + geom_violin() +geom_jitter(alpha=0.3)
box_visual + geom_beeswarm(aes(color=Species))
```

#Q6
```{r}
#6.1
iris_dt
ggplot(iris_dt, aes(x=Petal.Length, y=Petal.Width,color=Species) )+ geom_point() + theme_bw() +labs(x="Petal Length", y="Petal With", title="Relationship Between Petal Length and Width")
```

#Q7
```{r}
anscombe_reshaped<-anscombe %>%
as.data.table %>%
.[, ID := seq(nrow(.))] %>%
melt(id.var=c("ID")) %>%
separate(variable, c('xy', 'group'), sep=1) %>%
  dcast(... ~ xy) %>% .[, group := paste0("dataset_", group)]

summary(anscombe_reshaped)
anscombe_reshaped[, .(y_std = sd(y), x_std=sd(x))]

anscombe_reshaped[, group:=as.factor(group)]
#7.2
anscombe_reshaped[, .(corr=cor(x,y)), by=group]

#7.3
ggplot(anscombe_reshaped, aes(x=x, y=y)) + geom_point() + facet_wrap(~group)
```


#Q8
```{r}
## copy-pasted code
mtcars <- data.table(mtcars)
## First compute median
mtcars[, medians := median(mpg), by = cyl]
## Quantiles
mtcars[, c("lq", "uq") := .(quantile(mpg, 0.25), quantile(mpg, 0.75)), by = cyl]
## Whiskers
mtcars[, IQR := 1.5 * IQR(mpg), by = cyl]
mtcars[, c("up_IQR", "down_IQR") := .(IQR + uq, lq - IQR)]
## Get the most extreme value within 1.5*IQR
mtcars[mpg < up_IQR,
up_whisker := max(mpg),
by = "cyl"]
mtcars[mpg > down_IQR,
down_whisker := min(mpg),
by = "cyl"]
## Compute outliers
mtcars[, outlier := (mpg < down_IQR | mpg > up_IQR), by = 'cyl']
ggplot(mtcars, aes(cyl, medians, ymax = uq, ymin = lq)) +
geom_crossbar(fill = 'white', width = 1.3) +
geom_segment(aes(cyl, down_whisker, xend = cyl, yend = lq)) +
geom_segment(aes(cyl, uq, xend = cyl, yend = up_whisker)) +
geom_point(data = mtcars[outlier == TRUE], aes(cyl, mpg))
```

